Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-13 paper.qmd
Added Figure 9 title

```{r}
#| label: fig-rm-lg
#| fig-cap: "\\gD{} Vs $7\\text{-}D$ distance between the bin centroids and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal: (b) benchmark = 6.5$a_1$ and (c) benchmark = 2$a_1$, where $a_1$ = 0.03."
#| fig-height: 15
#| fig-width: 15

>>>>

```{r}
#| label: fig-rm-lg
#| fig-cap: "The choice of long edge removal significantly impacts the model's accuracy. \\gD{} Vs $7\\text{-}D$ distances between the bin centroids, where the model is fitted with UMAP for the non-linear cluster data. The two benchmarks for long edge removal: (b) benchmark = 6.5$a_1$ and (c) benchmark = 2$a_1$, where $a_1$ = 0.03 are made. The wireframes in \\gD{} and a projection from $7\\text{-}D$ are shown with Delaunay triangulation (a1, a2) and the two benchmark values (b1, b2, c1, c2). With the benchmark set at 6.5$a_1$, long edges exist within the C-shaped cluster, which distrupts the model. In contrast, using 2$a_1$ is a better option, as it effectively captures the non-linear shapes of the clusters. To generate an accurate model that captures the data structure, the choice of long edge removal does matter."
#| fig-height: 15
#| fig-width: 15
